Label object representation and manipulation with ITK

### 2009-07-01 article/Article.tex
add the contribution of a single pixel to the central moment computation as done by Dirk Padfield in http://insight-journal.com/download/viewpdf/301/4/download, but with taking spacing into account
Ignore-this: cfe8218dfdb1a0aeaa06dc05eedcd1bc

darcs-hash:20090701150858-2fc9d-47f310f489ed1b001fdc9b856b8efcb6f48d6d86.gz

>>>>

A constant must be added when both elements of the second order moment are 
the same. This constant represents the normalized second order central moment of a pixel. This is required 
because the measurements are based on discrete pixels rather than continuous values. The normalized 
second order central moment of a pixel with unit length of a binary image can be found as:

$M_{000} = \int_{0}^{\delta_{x}}\int_{0}^{\delta_{y}}\int_{0}^{\delta_{z}}dzdydx = \delta_{x}\delta_{y}\delta_{z} = \Delta$

$M_{100} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}x dzdydx = \delta_{y}\delta_{z}\left[\frac{x^2}{2}\right]_{0}^{\delta{x}} = \frac{\delta_{x}\Delta}{2}$

$M_{110} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}xy dzdydx = \delta_{z}\left[\frac{x^2}{2}\right]_{0}^{\delta{x}}\left[\frac{y^2}{2}\right]_{0}^{\delta{y}} = \frac{\delta_{x}\delta_{y}\Delta}{4}$

$M_{200} = \int_{0}^{\delta{x}}\int_{0}^{\delta{y}}\int_{0}^{\delta{z}}x^{2} dzdydx = \delta_{y}\delta_{z}\left[\frac{x^3}{3}\right]_{0}^{\delta{x}} = \frac{\delta_{x}^{2}\Delta}{3}$

$\bar{x} = \frac{M_{100}}{M_{000}} = \frac{\frac{\delta_{x}\Delta}{2}}{\Delta} = \frac{\delta_{x}}{2}$
$\bar{y} = \frac{M_{010}}{M_{000}} = \frac{\frac{\delta_{y}\Delta}{2}}{\Delta} = \frac{\delta_{y}}{2}$

$\mu'_{110} = \frac{M_{110}}{M_{000}} - \bar{x}\bar{y} = \frac{\frac{\delta_{x}\delta_{y}\Delta}{4}}{\Delta} - \frac{\delta_{x}}{2}*\frac{\delta_{y}}{2} = \frac{\delta_{x}\delta_{y}}{4} - \frac{\delta_{x}\delta_{y}}{4} = 0$

$\mu'_{200} = \frac{M_{200}}{M_{000}} - \bar{x}^{2} = \frac{\frac{\delta_{x}^{2}\Delta}{3}}{\Delta} - (\frac{\delta_{x}}{2})^{2} = \frac{\delta_{x}^{2}}{3} - \frac{\delta_{x}^{2}}{4} = \frac{\delta_{x}^{2}}{12}$

Thus, the second order cross moment is 0, and the second order moment is 12 . A straightforward analysis 
holds for other dimensions. This explains why it is necessary to add a scalar 1 
12 to each normalized second 
order central moment when the indices are the same dimension and it is not necessary to add anything for 
normalized second order central moments consisting of cross moments.
